### 2015-04-02 TODO.Rmd
update

* Use permanent e-mails instead of Williams e-mails.

>>>>

* Format vignette as The R Journal submission
* Make examples run quickly
* Get rid of lots of useless functions like view_growth and plot_quality. This is overkill. We might use versions of these functions in the article. But we don't need them to be user functions.
* Get rid of qmj class material.
* Fix NOTE about the misuse of Imports
* Take care of issues raised in R CMD check.
